Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-22 paper.qmd
feat: add new point about "Incomplete Reproducibility"

>>>>

5. Incomplete Reproducibility: Reproducibility should be understood as a spectrum
  rather than a binary property, a notion emphasised in "Reproducibility in Software
  Engineering" by @dellaieraMasterThesis2024. Docker illustrates this spectrum well:
  it provides strong run-time reproducibility—that is, consistency in space
  (where the same image behaves identically across different systems) but weak
  build-time reproducibility, which concerns consistency over time. As defined in
  the thesis, reproducibility at build time means being able to produce an identical
  build artefact regardless of when or where it is built. However, Docker inherently
  fails to guarantee this property. Its reliance on mutable base images and non-deterministic
  instructions such as `apt-get update` leads to temporal drift: rebuilding the same
  `Dockerfile` at different points in time can produce distinct outputs. In the
  experimental evaluation conducted in the thesis, even with pinned base images,
  checksums of the resulting containers varied across builds and machines. Thus, while
  Docker offers partial reproducibility: strong at run time (space) and weak at build time (time),
  it cannot on its own ensure verifiable, deterministic software artefacts. Achieving
  true reproducibility requires pinning image digests, freezing dependency versions,
  and employing deterministic build systems such as Nix or Guix for complete control
  over both space and time [@Malka_2024].
